Data Cleaning

### 2024-11-28 study1/analysis/1_cleaning.qmd
Update 1_cleaning.qmd

```{r}
#/ output

@@

df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

@@

```{r}
#/ code-fold: TRUE

@@

```{r}
#/ code-fold: TRUE

# Education 
# did not add education disiplines

p_edu <- df |>
  mutate(Education = fct_relevel(Education, "Secondary (technical) School", "Elementary School", "High School", "Bachelor", "Master", "Doctorate")) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Education)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  # scale_fill_viridis_d(guide = "none") +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
  theme_modern(axis.title.space = 15) +
   scale_fill_manual(values = c("Secondary (technical) school"="#0571B0","High school"= "#d01c8b", "Bachelor"="#FDB863", "Master"="#E66101", "Doctorate" =  "#ca0020")) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5)),
    axis.title.x = element_blank()
  )

@@

## Ethinicity

```{r}
#/ code-fold: TRUE
# Ethnicity

p_eth <- df |>
  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
  ggplot(aes(x = Ethnicity)) +
  geom_bar(aes(fill = Ethnicity)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
  theme_modern(axis.title.space = 15) +
  scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.6)),
    axis.title.x = element_blank())

@@

```{r}

@@

p_cou <- df |>
  mutate(Country = fct_relevel(Country,"United Kingdom", "Ireland", "USA", "Australia")) |>
  ggplot(aes(x = Country)) +
  geom_bar(aes(fill = Country)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Country of Residence", y = "Number of Participants", subtitle = "Participants per Country they are currently living") +
  theme_modern(axis.title.space = 15) +
  scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.7)),
    axis.title.x = element_blank())

@@

```{r}

# <!--Do it-->

@@

```{r}
# Create mapping from df's country names to world_map's country names. I think the map is not working because the names do not match.

country_mapping <- data.frame(
  df_name = c("United States", "United Kingdom"),
  world_map = c("USA", "UK") 
)

country_mapping

\## Experiment Enjoyment

```{r}

>>>>

```{r}
#| warning: false
#| code-fold: true
#| error: false

@@

#df <- read_csv("C:/Users/emmal/OneDrive - University of Sussex/GitHub/Placement/InteroceptionScale/study1/data/rawdata_participants.csv")

df <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionScale/refs/heads/main/study1/data/rawdata_participants.csv")
```

@@

```{r}
#| warning: false
#| code-fold: true
#| error: false

@@

```{r}
#| warning: false
#| code-fold: true
#| error: false

# did not add education disiplines

p_edu <- df |>
  mutate(Education = fct_relevel(Education, "Secondary (technical) School", "Elementary School", "High School", "Bachelor", "Master", "Doctorate")) |>
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Education)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
  theme_modern(axis.title.space = 15) +
  # scale_fill_manual(values = c("Secondary (technical) school"="#0571B0","High school"= "#d01c8b", "Bachelor"="#FDB863", "Master"="#E66101", "Doctorate" =  "#ca0020")) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.5), angle = 45, hjust =1),
    axis.title.x = element_blank()
  )

@@

## Ethnicity

```{r}
#| warning: false
#| code-fold: true
#| error: false

# Ethnicity

p_eth <- df |>
  mutate(Ethnicity = fct_relevel(Ethnicity,"East Asian", "Mixed", "White", "Black", "persian", "South Asian", "Hispanic/Latino")) |>
  ggplot(aes(x = Ethnicity)) +
  geom_bar(aes(fill = Ethnicity)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Ethnicity", y = "Number of Participants", subtitle = "Participants per Ethnicity") +
  theme_modern(axis.title.space = 15) +
  #scale_fill_manual(values = c("East Asian"="#0571B0","Mixed"= "#d01c8b", "White"="#cc66cc", "Black"="#E66101", "persian" =  "#ca0020", "South Asian"="#5E3C99", "Hispanic/Latino"="#92C5DE")) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.6), angle = 45, hjust = 1),
    axis.title.x = element_blank())

@@

```{r}
#| warning: false
#| code-fold: true
#| error: false

@@

p_cou <- df |>
  mutate(Country = fct_relevel(Country,"United Kingdom", "Ireland", "USA", "Australia")) |>
  ggplot(aes(x = Country)) +
  geom_bar(aes(fill = Country)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Country of Residence", y = "Number of Participants", subtitle = "Participants per Country they are currently living") +
  theme_modern(axis.title.space = 15) +
  #scale_fill_manual(values = c("United Kingdom"="#ca0020","Ireland"= "#d01c8b", "United States"="#FDB863", "Australia"="#E66101"))+
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(0.7),  angle = 45, hjust =1),
    axis.title.x = element_blank())

@@

```{r}
#| warning: false
#| code-fold: true
#| error: false

@@

## Experiment Enjoyment

```{r}
#| warning: false
#| code-fold: true
#| error: false
